Mendelian randomization for causal inference in genome-wide association studies

### 2022-03-04 mr-review.Rmd
updated yaml & started method.xlsx

---
title: "Mendelian randomization for causal inference in genome-wide association studies"
author: "Frederick J. Boehm & Xiang Zhou"
date: "`r lubridate::now()`"
bibliography: exported.bib
csl: elsevier-with-titles.csl
link-citations: yes
linkcolor: blue
output: 
  - bookdown::pdf_document2
  - bookdown::html_document2
  - bookdown::word_document2
---

>>>>

---
title: "Mendelian randomization for causal inference in genome-wide association studies"
author: "Frederick J. Boehm & Xiang Zhou"
date: "`r lubridate::now()`"
bibliography: exported.bib
csl: elsevier-with-titles.csl
link-citations: yes
linkcolor: blue
always_allow_html: true
output: 
  - bookdown::pdf_document2
  - bookdown::html_document2
  - bookdown::word_document2
---
